%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	11pt, % Default font size, can use 10pt, 11pt or 12pt
]{cv} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font
\usepackage[dvipsnames]{xcolor} % for color of linkedin logo
\usepackage[hidelinks]{hyperref} % For links
\usepackage{orcidlink}
\usepackage{fontawesome} % For LinkedIn logo

%------------------------------------------------

\name{Madeleine E. Goertz} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.

%\address{San Luis Obispo, CA} % Main address
\address{\normalsize Curriculum Vitae}
\address{\href{mailto:mgoertz@calpoly.edu}{mgoertz@calpoly.edu} \\
\orcidlinkc{0000-0001-6740-7372} \\ 
\href{https://madeleinegoertz.github.io/}{madeleinegoertz.github.io} 
 } % A secondary address (optional)


%----------------------------------------------------------------------------------------

\begin{document}

\begin{rSection}{Education}
	\textbf{California Polytechnic State University}, San Luis Obispo, CA \hfill Sept. 2021 -- June 2025 \\
	Master of Science in  Mathematics \hfill \textit{GPA: 4.0/4.0} \\
	\-\hspace{1cm}Advised by Patrick Orson, wrote Master's Thesis \href{https://digitalcommons.calpoly.edu/theses/3005/}{\textit{On Diffeomorphism Groups of Surfaces}}\\
	Bachelor of Science in Mathematics \hfill \textit{GPA: 4.0/4.0} \\
	\-\hspace{1cm}Advised by Eric Brussel, wrote Senior Project \textit{On Moduli Spaces of Triangles}
	% Joint BS/MS Program. Member of University Honors Program, Association for Women in Mathematics
\end{rSection}

\begin{rSection}{Preprints \& Publications}
	\begin{rSubsectionNumbered}{Journal Articles}
		\item The Torus of Triangles. (with E. Brussel). (to appear in \emph{Involve, A Journal of Mathematics}).	\href{http://arxiv.org/abs/2303.11446}{arXiv:2303.11446}.	
	\end{rSubsectionNumbered}
	\begin{rSubsectionNumbered}{Conference Proceedings}
		\item Exhaustive Generation of Pattern-Avoiding $s$-Words. (with S. Buick, A. Lastmann, K. Pal, H. Qian, S. Tacheny, A. Williams, L. Williams, and Y. Zhai). (to appear in \textit{Proceedings of the 23rd International Conference on Permutation Patters, 2025}). \href{https://www.researchgate.net/publication/391522113_Exhaustive_Generation_of_Pattern-Avoiding_s-Words}{Link to \underline{Research Gate Preprint}}.
	\end{rSubsectionNumbered}
	\begin{rSubsectionNumbered}{Preprints}
		\item The Quaternary Gray Code and How It Can Be Used to Solve Ziggurat and Other Ziggu Puzzles. (with A. Williams).\\ \href{http://arxiv.org/abs/2411.19291}{arXiv:2411.19291}. (preprint).
		\item The Stack of Triangles Up to Similarity. (with E. Brussel, E. Guptill, \& K. Lyle). \href{http://arxiv.org/abs/2408.07792}{arXiv:2408.07792}. (preprint).		
	\end{rSubsectionNumbered}
\end{rSection}
\begin{rSection}{Selected Awards \& Scholarships}
	Academic Excellence Award, Cal Poly Bailey College of Science and Mathematics \dotfill May 2025 \\
	Academic Excellence Award, Cal Poly Math Department \dotfill May 2025 \\
	Charles J. Hanks Excellence in Mathematics Scholarship \dotfill May 2024 \\
	% \-\hspace{1cm}\textit{Awarded to the top student in the Cal Poly math department.}\\
	Frost Research Scholarship \dotfill Sept. 2022 -- June 2025 \\
	% \-\hspace{1cm}\textit{College of Science and Math Award to support research, \$10,000 per year for 3 years. Part of inaugural cohort of scholars.}\\
	First place, Physical \& Mathematical Sciences, 37th Annual CSU Student Research Competition \dotfill Apr. 2023 \\
	% \-\hspace{1cm}\textit{California State University system-wide competition for 10-minute research talk to a general audience.} \\
	Frost Summer Undergraduate Research Scholarship \dotfill June 2022 \& June 2023
	% \-\hspace{1cm}\textit{Stipend to support summer research. \$4,500 per summer for two summers.}
	% Michael Hushour Scholarship \dotfill May 2024 \\
	% Bryant Russel Memorial Award \dotfill May 2024 \\
	% First place, Cal Poly Three Minute Thesis Competition \dotfill Feb. 2024 \\
	% Cal Poly Bailey College of Science and Mathematics Standout Student \dotfill Nov. 2023 \\
	% Women in STEM Scholarship \dotfill May 2023 \\
	% Advancement of Science \& Technology Scholarship \dotfill May 2023 \\
	% Edward Van Duyne Memorial Scholarship \dotfill May 2022 \\
	% Math and Science Teacher Initiative Initial Scholarship \dotfill Sept. 2022
\end{rSection}

\begin{rSection}{Research Program Participation}{}{}{}
	NSF SMALL REU, \textit{Williams College} \dotfill Summer 2024 \\
	\-\hspace{1cm}Advised by Aaron Williams, on \textit{Combinatorial Algorithms \& Hamilton Paths} \\
	Frost Summer Undergraduate Research Program, \textit{Cal Poly} \dotfill Summer 2023 \\
	\-\hspace{1cm}Advised by Eric Brussel, on \textit{Moduli Space of Triangles} \\
	Frost Summer Undergraduate Research Program, \textit{Cal Poly} \dotfill Summer 2022 \\
	\-\hspace{1cm}Advised by Eric Brussel, on \textit{Poncelet's Theorem}
\end{rSection}

\begin{rSection}{Selected Research Communication}

	\begin{rSubsectionNumbered}{Talks for Mathematical Audiences}
		\item ``Solving Ziggu Puzzles Using the Quaternary Gray Code.'' (with A. Williams). CM16 - Greedy Constructions of Gray Codes, \textit{CanaDAM 2025: Canadian Discrete and Algorithmic Mathematics Conference}, Ottawa, CA, May 2025. (virtual talk).
		\item ``Moduli Space of Triangles \& Euclid's Similarity Theorems." (with E. Brussel, E. Guptill, \& K. Lyle). AMS Contributed Paper Session on Geometry, \textit{ Joint Mathematics Meetings},
		San Francisco, CA. Jan. 2024.
		\item ``Geometry of the moduli spaces of similarity classes of triangles defined by three classical theorems." (with E. Brussel, E. Guptill, \& K. Lyle). \textit{ 2nd CSU Mathematical Sciences Conference},
		Bakersfield, CA. Nov. 2023.
		\item ``Poncelet Families \& The Torus of Triangles." (with E. Brussel). \textit{1st CSU Mathematical Sciences Conference},
		Northridge, CA. Nov. 2022.
	\end{rSubsectionNumbered}
	% \newpage
	\begin{rSubsectionNumbered}{Talks for General Audiences}
		\item ``Solving Ziggu Puzzles Using the Quaternary Gray Code.'' (with A. Williams). \textit{Cal Poly Bailey College of Science and Mathematics Student Research Conference}, San Luis Obispo, CA. May 2025.
		\item ``A Moduli Space of Triangles." (with E. Brussel). \textit{4th Annual CSU Grad Slam},
		Virtual Meeting. May 2024.
		% \item ``A Moduli Space of Triangles." (with E. Brussel). \textit{Western Association of Graduate Schools 8th Annual Regional Three Minute Thesis Competition},
		% Virtual Meeting. Mar. 2024.
		% \item ``A Moduli Space of Triangles." (with E. Brussel). \textit{Cal Poly Three Minute Thesis Competition},
		% San Luis Obispo, CA. Feb. 2024.
		% \item ``The Torus of Triangles." (with E. Brussel).\textit{ Cal Poly College of Science and Mathematics Research Conference},
		% San Luis Obispo, CA. May 2023.
		\item ``The Torus of Triangles." (with E. Brussel). \textit{ 37th Annual CSU Student Research Competition},
		San Diego, CA. Apr. 2023.
		% \item ``The Torus of Triangles." (with E. Brussel). \textit{Cal Poly CSU Student Research Competition},
		% San Luis Obispo, CA. Feb. 2023.
	\end{rSubsectionNumbered}
	\begin{rSubsectionNumbered}{Poster Presentations}
		\item ``Three Moduli Spaces of Triangles." (with E. Brussel, E. Guptill, \& K. Lyle).  \textit{Bailey College of Science and Mathematics 2024 Student Research Conference}, San Luis Obispo, CA. May 2024.
		% \item ``Three Moduli Spaces of Triangles." (with E. Brussel, E. Guptill, \& K. Lyle). \textit{Cal Poly Summer Undergraduate Research Symposium}, San Luis Obispo, CA. Oct. 2023.
		% \item ``Three Moduli Spaces of Triangles." (with E. Brussel, E. Guptill, \& K. Lyle). \textit{Mathematics Department Summer Research Poster Symposium}, San Luis Obispo, CA. Oct. 2023.
		\item ``Poncelet Families \& The Torus of Triangles." (with E. Brussel). \textit{ Mathematics Department Summer Research Poster Symposium}, San Luis Obispo, CA. Oct. 2022.
	\end{rSubsectionNumbered}

	
\end{rSection}

% \newpage
\begin{rSection}{Teaching Experience}
	Teaching experience as a graduate teaching associate and instructor of record.

	Math 221: Calculus for Business and Economics, \textit{Cal Poly}\dotfill Spring Quarter 2025 \\
	Math 118: Precalculus Algebra, \textit{Cal Poly} \dotfill Fall Quarter 2024, Winter Quarter 2025
\end{rSection}

\begin{rSection}{Other Work Experience}
	Mathematics Tutor, \textit{Cal Poly Learning Support Center} \dotfill Oct. 2023 -- June 2024 \\
	Grader, \textit{Cal Poly Department of Mathematics} \dotfill Jan. 2023 -- June 2023 \\
	Learning Assistant, \textit{Cal Poly Department of Physics} \dotfill Apr. 2022 -- June 2022 \\
	Coding Camp Instructor, \textit{Coding with Kids LLC} \dotfill June 2019 -- Sept. 2021
\end{rSection}

% \begin{rSection}{Conference \& Competition Attendance}
% 	Bailey College of Science and Mathematics Student Research Conference, \textit{San Luis Obispo, CA} \dotfill May 2024 \\
% 	4th Annual CSU Grad Slam Competition, \textit{Virtual} \dotfill May 2024 \\
% 	8th Annual Western Association of Graduate Schools Regional 3-Minute Thesis Competition, \textit{Virtual} \dotfill Mar. 2024 \\
% 	2024 Joint Mathematics Meetings, \textit{San Francisco, CA} \dotfill Jan. 2024 \\
% 	2nd CSU Mathematical Sciences Conference, \textit{Bakersfield, CA} \dotfill Nov. 2023 \\
% 	Cal Poly College of Science and Mathematics Research Conference, \textit{San Luis Obispo, CA} \dotfill May 2023 \\
% 	37th Annual CSU Student Research Competition, \textit{San Diego, CA} \dotfill Apr. 2023 \\
% 	2023 Joint Mathematics Meetings, \textit{Boston, MA} \dotfill Jan. 2023 \\
% 	1st CSU Mathematical Sciences Conference, \textit{Northridge, CA} \dotfill Nov. 2022
% \end{rSection}

\begin{rSection}{Leadership \& Involvement}
	Member, \textit{Simple Group Seminar} \dotfill Sept. 2021 -- June 2025 \\
	Member, \textit{Cal Poly Association for Women in Mathematics Chapter} \dotfill Sept. 2021 -- June 2025 \\
	Member, \textit{Cal Poly Math Club} \dotfill Sept. 2021 -- June 2025 \\
	Ambassador, \textit{Cal Poly University Honors Program} \dotfill Feb. 2023 -- June 2024 \\
	Member, \textit{Cal Poly National and International Fellowships \& Scholarships Advisory Board} \dotfill Feb. 2025 -- June 2025 
\end{rSection}

\begin{rSection}{Skills}
	\textbf{Technical: } Mathematica, Java, Python, R, Git.\\
	\textbf{Nontechnical: } English, German, Mathematics Communication.
\end{rSection}

\end{document}
